Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-28 WSSSPE2_report/WSSSPE2_review.tex
Add in missing periods at the end of two lists.

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who do not now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors (e.g., Project
Credit~\cite{projectcredit}) tied to places that these metrics are already
stored (e.g., ORCID~\cite{orcid})
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

@@

After the first breakout session, the groups A and B came together and discussed
a rollup of the ideas from the subgroups at a high level:
\begin{itemize}
\item citation ecosystem - traces of usage (metrics)
\item taxonomy of contributorship, understanding roles
\item prizes
\item new metrics (for people's activities in software)
\item guidelines for evaluating scientific contribution through software (perhaps 
using new metrics)
\end{itemize}

>>>>

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who do not now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors (e.g., Project
Credit~\cite{projectcredit}) tied to places that these metrics are already
stored (e.g., ORCID~\cite{orcid})
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement.
\end{itemize}

@@

After the first breakout session, the groups A and B came together and discussed
a rollup of the ideas from the subgroups at a high level:
\begin{itemize}
\item citation ecosystem - traces of usage (metrics)
\item taxonomy of contributorship, understanding roles
\item prizes
\item new metrics (for people's activities in software)
\item guidelines for evaluating scientific contribution through software (perhaps 
using new metrics).
\end{itemize}
